---
title: "In-class assignment"
author: "Sinan Ocaktan"
date: "`r format(Sys.time(), '%d %B %y')`"
---

```{r include = FALSE}
library(tidyverse) 
library(lubridate)
library(nycflights13)
library(ggplot2)
library(knitr)

df <- planes

```

## NYC Flights
Here we can take a look at our dataset.

```{r}

kable(head(df))

```



### Part 1
#### Calculation

We can calculate the mean seat number on flights changing by the year and visualize them on a plot. We filter out older than 1985 to get more stable results.

```{r}

seats <- df %>% group_by(year) %>% dplyr::summarize(Mean = mean(seats),) %>% filter(year > 1985)
seats[order(seats$year),]
```

#### Visualization

```{r}

ggplot(data=seats,aes(x=year,y=Mean)) +
  geom_line()

```
In the early 2000s, mean seat numbers decreased significantly. **Note that y-axis does not start from zero**


### Part 2
#### Calculation

We can calculate the change in the preference of manufacturors by the year.


```{r}

man = df %>% count(manufacturer, year, sort = TRUE) %>% filter(n > 10)
man
```
#### Visualization

```{r}

ggplot(data=man,aes(x=year,y=n,color=manufacturer)) +
  geom_line()

```
We can see the popularity of the manufacturers changing by the year.
